\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\renewcommand\arraystretch{1.2}
\usepackage{enumitem}
\usepackage{version}  % For exam vs solutions
\usepackage{parskip}
\input{definitions.tex}

\begin{document}
\excludeversion{solution} \includeversion{blankpages}
% \includeversion{solution} \excludeversion{blankpages}


\begin{minipage}[c]{0.45\textwidth}
{Instructor\\
Prof.\ B.\ Stellato}
\end{minipage}
\hfill
\begin{minipage}[c]{0.45\textwidth}
    {\begin{flushright}
		    AIs\\ I.\ Wang, V.\ Ranjan, S.\ Clarke, J.\ Ge
    \end{flushright}}
\end{minipage}

\vspace{3em}

\begin{center}
	\Large\bf ORF307: Optimization\\[.75em]
	\large\bf Spring 2023 Final Exam \begin{solution}Solutions\end{solution}\\[.5em]
\bf May 12, 11:00am -- 12:20pm
\end{center}

\vspace{4em}


\begin{center}
	\bf Exam Rules
\end{center}
\begin{enumerate}
	\item Please write out and sign the following pledge at the bottom of this page:  ``I pledge my honor that I have not violated the Honor Code or the rules specified by the
instructor during this exam.''
	\item You are allowed a single sheet of paper, double-sided, hand-written or typed.
	\item You cannot communicate with anyone during the exam.
	\item All questions should be answered in the solution booklet. Write your name on every page that you use to write the solutions. Start each problem on a separate page. Answering multiple subparts of the same problem on the same page is fine.
	\item There are 3 problems worth a total of 100 points.
\end{enumerate}

\vspace{5em}
\textbf{Name:} \hrulefill  \\*[1em]
\textbf{Honor code:} \hrulefill\\
\rule{\textwidth}{0.4pt}
\rule{\textwidth}{0.4pt}
\rule{\textwidth}{0.4pt}
\vfill


\begin{enumerate}


\newpage
\item \emph{Question (30 points).}
Description....
\begin{enumerate}
	\item Task 1
	\item Task
\end{enumerate}


\begin{solution}\textbf{Solution.}
\begin{enumerate}
	\item Solution
	\item Solution
	\item Solution
\end{enumerate}
\end{solution}


\newpage
\begin{blankpages}
\null\newpage
\null\newpage
\end{blankpages}


\item \emph{Other question (XX points).}
\begin{enumerate}
	\item Task 1
\end{enumerate}



\begin{solution}\textbf{Solution.}
\begin{enumerate}
	\item Sol 1
\end{enumerate}
\end{solution}
\newpage
\begin{blankpages}
\null\newpage
\null\newpage
\end{blankpages}





\end{enumerate}
\end{document}
